\documentclass[11pt]{article}
\usepackage{fullpage}
\usepackage{amsmath,amsfonts,amsthm,amssymb}
\usepackage{url}
\usepackage[demo]{graphicx}
\usepackage{caption} 
\usepackage{algpseudocode}
\usepackage{bbm}
\usepackage{float}
\usepackage{framed}
\usepackage{enumerate}
\usepackage{color}
\usepackage{mathtools}
\usepackage[colorlinks=true, linkcolor=red, urlcolor=blue, citecolor=blue]{hyperref}

\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\renewcommand\qedsymbol{$\blacksquare$}

\usepackage{amsthm}

\DeclareMathOperator*{\E}{\mathbb{E}}
\let\Pr\relax
\DeclareMathOperator*{\Pr}{\mathbb{P}}
\DeclareMathOperator*{\R}{\mathbb{E}}

\topmargin 0pt
\advance \topmargin by -\headheight
\advance \topmargin by -\headsep
\textheight 8.9in
\oddsidemargin 0pt
\evensidemargin \oddsidemargin
\marginparwidth 0.5in
\textwidth 6.5in

\parindent 0in
\parskip 1.5ex

\newcommand{\homework}[2]{
	\noindent
	\begin{center}
		\framebox{
			\vbox{
				\hbox to 6.50in { {\bf NYU Computer Science Bridge to Tandon Course} \hfill Winter 2021 }
				\vspace{4mm}
				\hbox to 6.50in { {\Large \hfill Homework 8  \hfill} }
				\vspace{2mm}
				\hbox to 6.50in { {Name: Danrong Li \hfill} NetID: dl4111}

			}
		}
	\end{center}
	\vspace*{4mm}
}

\begin{document}
	
	\homework{1}{Danrong Li}
	\section*{Question 7}
	
	Solve the following questions from the Discrete Math zyBook:
	
	\textbf{1. Exercise 6.1.5, section b-d}
	
	\textbf{b.}
	In three of a kind, 3 cards in the same rank and the other 2 cards has different ranks from the 3 cards and from each other. This means, the 3 cards can be chosen from 13 choices and the 2 cards would be to choose 2 from the remaining. In addition that there are 4 suits in a deck and the total number of options is to choose 5 from the 52 cards, we have the final answer:
	
    \textbf{13 * C(12,2) * C(4,3) * C(4,1) * C(4.1) / C(52,5)}
	
	\vspace{10mm}
	\textbf{c. }
	There are a total of 4 suits in a deck of card, and there are C(13,5) ways to choose 5 from 13 cards. In addition that the total number of options is to choose 5 from the 52 cards, we have the final answer:
	
	\textbf{C(4,1) * C(13,5) / C(52,5)}
	
	\vspace{10mm}
	\textbf{d.}
	In two of a kind, 2 cards have the same rank and the other 3 cards have different ranks from the 2 cards and from each other. In other words, the 2 cards can have 13 choices of ranks and the 3 cards can choose 3 from the 12 choices. n addition that there are 4 suits in a deck and the total number of options is to choose 5 from the 52 cards, we have the final answer:
	
	\textbf{13 * C(12,3) * C(4,2) * C(4,1) * C(4,1) * C(4,1) / C(52,5)}
	
	\vspace{10mm}
	\textbf{2. Exercise 6.2.4, sections a-d}
	
	\textbf{a.} 
	The probability of having at least one club is 1 - P(not have club). Excluding club, we have (52-13=) 39 cards. Thus we have the final answer:
	
	\textbf{1 - (C(39,5) / C(52,5))}
	
	\vspace{10mm}
	\textbf{b.}
	P(at least 2 cards with same rank) = 1 - P(no cards with same rank). We would first 5 ranks from 13 ranks and each rank has 4 choices in suit. 
	
	\textbf{Thus the final answer is:}
	$1-(((C(13,5))*((C(4,1))^5))/(C(52,5)))$
	
	\vspace{10mm}
	\textbf{c.}
	P(exactly 1 club or exactly 1 spade) = P(exactly 1 club) + P(exactly 1 spade) - P(exactly 1 club and exactly 1 spade). P(exactly 1 club) = P(exactly 1 spade) = choose 4 from (52-13=) 19 cards and the club could be from 13 choices. Similarly for both 1 club and 1 spade. Thus the final answer is:
	
	\textbf{(C(39,4) * 13 * 2 - C(26,3) * 13 * 13) / C(52,5)}

	
	\vspace{10mm}
	\textbf{d.}
	P(at least 2 clubs or at least 1 spade) = 1 - P(no club and no spade), thus the final answer is:
	
	\textbf{1 - C(26,5)/C(52,5)}
	
	\newpage
	\section*{Question 8}
	Solve the following questions from the Discrete Math zyBook:
	
	\textbf{1. Exercise 6.3.2, sections a-e}
	
	\textbf{a.}
	
	
	\vspace{10mm}
	\textbf{b.}
	

	
	\vspace{10mm}
	\textbf{c.}
	
	
	
	\vspace{10mm}
	\textbf{d.}

	
	\vspace{10mm}
	\textbf{e.}
	
	
	
	\vspace{10mm}
	\textbf{2. Exercise 6.3.6, sections b,c}
	
	\textbf{b.}
	
	
	\vspace{10mm}
	\textbf{c.}
	
	\vspace{10mm}
	\textbf{3. Exercise 6.4.2, section a}
	
	\textbf{a.}

	\newpage
	\section*{Question 9}
	Solve the following questions from the Discrete Math zyBook:
	
	\textbf{1. a.}
	
	
	\vspace{10mm}
	\textbf{1. b.}
	
	
	\vspace{10mm}
	\textbf{2. a.}
	
	
	\vspace{10mm}
	\textbf{3. a.}
	
	\vspace{10mm}
	\textbf{3. b.}
	
	\vspace{10mm}
	\textbf{4. a.}

	
	\newpage
	\section*{Question 10}
	Solve the following questions from the Discrete Math zyBook:
	
	\textbf{1. a.}

	\vspace{10mm}
	\textbf{1. b.}
	
	\vspace{10mm}
	\textbf{1. c.}
	
	\vspace{10mm}
	\textbf{1. d.}
	
	
	\vspace{10mm}
	\textbf{2. b.}
	
	
\end{document}